\section{Conclusion}
This project involved the design and development of a "Training Management System" (TrainingMS) to modernize and automate the management of professional training activities. By replacing manual paper and spreadsheet-based processes with a centralized web application, the project addressed critical issues such as data inconsistency, time inefficiency, and the lack of analytical tracking. 

The successful implementation of features like role-based access control, CRUD management of entities, and an interactive statistics dashboard demonstrates the value of the platform in improving organizational productivity and data reliability. The project served as a comprehensive exercise in full-stack development, integrating Spring Boot, React, and MySQL into a coherent and functional solution.

\section{Future Work}
While the current version of TrainingMS fulfills the core requirements, several areas for future development have been identified:
\begin{itemize}
    \item \textbf{Advanced Analytics}: Integrating machine learning models to predict future training needs based on employee performance data.
    \item \textbf{Automated Notifications}: Developing a notification engine to send automated reminders and certificates via email or SMS.
    \item \textbf{Mobile Application}: Creating a dedicated mobile version for participants to view their training history and upcoming sessions on the go.
    \item \textbf{Feedback System}: Implementing an evaluation module to collect and analyze participant feedback after each session.
\end{itemize}
These enhancements will further solidify TrainingMS as a comprehensive tool for workforce development and organizational growth.
